\large{\bf Looking forwards and backwards: dynamics and genealogies of locally regulated populations }

### 2023-05-12 forwards-and-backwards.tex
acknow

\section*{Acknowledgements}

\comment{Need to thank KAVLI, Paris Cit\'e, various funders}
IL is supported by the ANID/Doctorado en el extranjero doctoral scholarship, grant number 2018-72190055.
TTHL supported by the EPSRC Centre for Doctoral Training in Mathematics of Random Systems: Analysis, Modelling and Simulation (EP/S023925/1) and the Deutsche Forschungsgemeinschaft (DFG, German Research Foundation) under Germany's Excellence Strategy, EXC-2047/1-390685813.

>>>>

\paragraph{Acknowledgements:}
Thanks go to Gilia Patterson for identifying the ``clumping'' phenomenon,
and to Marcin Bownick and David Levin for useful discussions.
AME thanks everyone in MAPS at Universit\'e Paris Cit\'e for their hospitality
during the period in which much of this research took place.
AME and PLR also thank the Kavli Institute for Theoretical Physics
for their hospitality and birdwatching opportunities.
PLR was supported by the NIH NHGRI (grant \#HG011395),
IL by the ANID/Doctorado en el extranjero doctoral scholarship, grant \#2018-72190055,
and TTHL by the EPSRC Centre for Doctoral Training in Mathematics of Random Systems: Analysis, Modelling and Simulation (EP/S023925/1)
the Deutsche Forschungsgemeinschaft under Germany's Excellence Strategy, EXC-2047/1-390685813,
the Rhodes Trust and St.~John's College, Oxford.
